---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Fira+Code:wght@300..700&display=swap');

body, h2, p {
  color: #1f1f1f;
  font-family: "Fira Code", sans-serif;
}

body {
  max-width: 640px;
  margin: 0 auto;
  background-color: #fcefee;
  animation: fadeIn 0.75s ease-in;
}

p, h2 {
  background-color: #ffffff;
  border-radius: 6px;
  padding: 16px 20px;
  outline: 1px solid #dadada;
  margin: 16px 0px 16px 0px;
}

h2 {
  border-top: 12px solid #ea9290;
  text-align: center;
}

p {
  font-size: 1.0em;
}

img {
  display: block;
  margin: 16px auto;
  max-width: 100%;
  transition: transform 0.3s ease;
}

img:hover {
  transform: scale(1.02);
}

.banner {
  width: 100%;
  margin: 0;
  border-radius: 6px;
  transition: none;
}

.banner:hover {
  transform: none;
}

p:has(img.banner) {
  background-color: transparent;
  padding: 0;
}


@keyframes fadeIn {
  from { opacity: 0; }
  to { opacity: 1; }
}
```

![](https://lh7-rt.googleusercontent.com/formsz/AN7BsVBOo50MGe_JnHIfTUk5B3AwDEihDFdzwxrYSfqXQrfT7DCas7pgO-g8o8T0azgz3KmIx7wez6liRdW5Ake1Sv8NcEKCpSBFBRSCmJGegOrs6TLirNWVIF5M1qL4IaRzeMyt1mrdv-2v0dAem8Nc1Ot3zPT1deLo5AsgLKkfTYbYPUsJaCpnGwowwxmVqcfJxP6C4ZEnqtGE07PK=w1916?key=IJblmpBv0zOCSN2x1xGl7w){.banner}

## What are mutuals liking on Instagram Reels?

This report tracks observations of Instagram Reels that have been like by mutuals (people you follow who also follow you back). Data was logged over a couple of days using a Google Form that captured the content category, recording format, likes, views, and duration of each reel observed.

```{r}
library(tidyverse)

options(scipen = 999)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQng-3GIUldqHQO-VWV2hB5-qA5nf9_KFnvaQfE311kEKpUZw9oS_AIYK_bpZgVVCasIM7PgTPhWFLS/pub?gid=500751628&single=true&output=csv")

latest_data <- rename(
  logged_data,
  content_category = 2,
  recording_format = 3,
  likes = 4,
  views = 5,
  duration = 6)


total_observations <- nrow(latest_data)


# Content Category Data
latest_data_longer <- latest_data |>
  separate_rows(content_category, sep = ", ")

common_content_category <- latest_data_longer |>
  count(content_category) |>
  slice_max(n)

most_common_content_category_name <- common_content_category$content_category
most_common_content_category_count <- common_content_category$n


# Recording Format Data
common_recording_format <- latest_data |>
  count(recording_format) |>
  slice_max(n)

most_common_recording_format_name <- common_recording_format$recording_format
most_common_recording_format_count <- common_recording_format$n


# Likes can be NA as not required in form due to Instagram reel creators turning 
# likes visibility off
mean_likes <- mean(latest_data$likes, na.rm = TRUE)
mean_views <- mean(latest_data$views)
mean_duration <- mean(latest_data$duration)
```

Based on **`r total_observations`** observations logged over a couple of days the average reels had **`r format(round(mean_likes), big.mark = ",")`** likes with **`r format(round(mean_views), big.mark = ",")`** views and duration of **`r round(mean_duration, 1)`** seconds.

The bar chart below shows the distribution of content categories observed across all logged reels. With the most popular category being **`r most_common_content_category_name`** at a total of **`r most_common_content_category_count`**.
```{r}
GRAPH_THEME <-theme(
  plot.title = element_text(family = "mono", face = "bold", size = 14, hjust = 0.5),
  axis.title = element_text(family = "mono", face = "bold", size = 11),
  axis.text = element_text(family = "mono", face = "bold", size = 11),
  axis.text.x = element_text(angle = 90, hjust = 1),
  panel.grid.major.x = element_blank())

# Content Category Graph
ggplot(data = latest_data_longer) +
  geom_bar(
    aes(x = content_category, fill = content_category),
    show.legend = FALSE) +
  labs(
    title = "Content Categories of Mutual Liked Reels",
    x = "Content Category",
    y = "Count") +
  theme_minimal() +
  GRAPH_THEME
```

The chart below displays the recording formats used in reels that were like by mutuals. The most dominate category was **`r most_common_recording_format_name`** at a total of **`r most_common_recording_format_count`**.
```{r}

# Recording Format Graph
ggplot(data = latest_data) +
  geom_bar(
    aes(x = recording_format, fill = recording_format),
    show.legend = FALSE) +
  labs(title = "Recording Formats of Mutual Liked Reels",
       x = "Recording Format",
       y = "Count") +
  theme_minimal() +
  GRAPH_THEME
```
